\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Gayoun}{Han}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%z
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Experienced software developer with a passion for collaboration and diverse tech stacks.}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +82 1022392233 & \enspace hello.gayuna@gmail.com & \enspace \faHome\enspace Seoul, South Korea \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/gayuna}{in/gayuna} &
\faGithub\enspace \color{blue} \href{https://gayuna.github.io}{gayuna.github.io} & \enspace {$\mathbb{X}$}\enspace \color{blue} \href{https://x.com/hello\_gayuna}{x.com/hello\_gayuna}
\end{tabular}
\end{center}
\section{Profile}
{Experienced in integrating internal and external systems,
adept at working with diverse tech stacks.}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Programming Language:} C/C++, Java/Kotlin, Python. ARM assembly}
\item {\textbf{Backend tech:} Spring Boot, Spring Batch, (S)FTP, Kafka, MySQL, HTTP, RESTful API}
\item {\textbf{Embedded tech:} Serial communications, Signal processing, Touch algorithm, Memory Map}
\item {\textbf{Others:} AWS, vscode, IntelliJ, Git, SVN, GitHub, GitLab, Gerrit, Jenkins, Circle CI}
\end{itemize}}

\section{Professional Experience}
\customcventry{10/2023 ‐ present}{{\color{blue}}{(TW Engineering @ eCommerce engineering)}}{Senior Back-end Engineer,}{Coupang, Inc.}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Integration with TW last-mile - Integrated with third-party delivery companies to facilitate customer deliveries in Taiwan. Overcame technical challenges, such as data timeouts during spikes in traffic, and successfully implemented the integration.
\item Integration with Forwarder, Custom brokers for US/KR to TW Jikgu - Integrate cross-border logistics and customs operations for international trade, collaborating with US, KR, and TW partners to facilitate sales in Taiwan
\item Integration with ChungHwa Telecom for safety number - Integrate with CHT to protect customers' privacy by replacing their phone number with a secure number.
\item Implement Multi-AZ environment - Setup resources and make a workflow to deployment for multiple AZs on AWS EC2	for high availability
\end{itemize}}}

\customcventry{10/2023 ‐ present}{{\color{blue}}{(Coupang Partner Integration Team @ FTS)}}{Senior Back-end Engineer,}{Coupang, Inc.}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Integrate with Forwarder, Custom brokers for Rocket Jikgu - Develop a system to streamline import/export \& custom clearance and last-mile delivery for US-KR Rocket Jikgu business. Reduced delivery time from 3 to 2 days, reduced costs, diversified export/import \& customs clearance for KR-TW Jikgu. Refactor codes to support multiple vendors and apply a single interface for improved efficiency.
\item Writing and running notification logic to send to TW customers - Create a notification service that utilizes shipping information as a trigger to send notifications via a variety of channels, including the Coupang app and SMS.
\item Integration of insurance for electronic devices - Maintain a system where if a customer purchases an insurance policy with a product, the insurance is activated according to the shipping status of the product and deactivated with the expiration.
\item Adopt CI pipeline - Integration of Sonarqube and Circle CI in-house with branch strategy
\item Optimize AWS costs - Reduce AWS costs by optimizing memory for applications in use and changing EC2 instance settings and types.
\end{itemize}}}

\customcventry{09/2019 ‐ 10/2021}{{\color{blue}}{(Memory Virtual Platform part@Design Verification Team)}}{Engineer,}{Samsung electronics}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Based on the User’s manual and SFR document, build an SW working like a controller IC that interacts with FW. This product lets FW development start earlier than FPGA.
\item Write a test script with the pytest to check functionalities based on NVMe spec, user’s manual, and SFR document.
\end{itemize}}}

\customcventry{06/2016 ‐ 09/2019}{{\color{blue}}{(Touch algorithm part@Display Solution Dev team)}}{Engineer,}{Samsung electronics}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Understand the concept of touch IC and develop an algorithm for accurate coordination and other requirements such as wake-up gestures.
\item Change algorithm code on the characteristics of each panel of smartphones.
\item Customer on-site support until mass production on various sites - Samsung, Sony, VIVO, OPPO, etc.
\item Implement additional features upon request from customers such as side sense for Sony.
\item Write a test script with the pytest to check functionalities based on the customer's standard.
\end{itemize}}}


\section{Education}
\customcventry{2010-2014}{\color{blue}\href{https://ewha.ac.kr/ewhaen/index.do}{Ewha Womans University}}{A bachelor's degree}{Seoul, South Korea}{}{}{Relevant Courses: Introduction of digital storytelling, Digital Media Technology, Media Interface, Basic Seminar in Digital Graphics, Digital Media Design, Digital Humanities, Computer Programming \& Lab, Mobile App Programming}
\customcventry{2012-2013}{\color{blue}\href{https://en.ritsumei.ac.jp/}{Ritsumeikan University}}{Exchange Student}{Kyoto, Japan}{}{}{Study in Kyoto Program 2012}

\section{Languages}
\begin{multicols}{3}
    \begin{itemize}[label=\textbullet]
    \item \textbf{Korean} [Native]
    \item {\textbf{English} [Fluent]}
    \item {\textbf{Japanese} [Fluent]}
    \end{itemize}
\end{multicols}
\end{document}